---
title: "Selection I"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Response to Selection

Response to selection (`R`), it is the difference of mean phenotypic value between the offspring of the selection parents and the whole of the parental generation before selection.

Selection differential (`S`), it is the mean phenotypic values of the individuals selected as parents expressed 
as a deviation from the population mean. 
$$
S = T_s - T
$$

```{r}
## simulate n individuals in parental population
n = 1000
parents <- rnorm(n)


## select top 5% of parents and random mate them
i = 0.05
p <- head(sort(parents, decreasing=TRUE), round(length(parents)*i,0))
k0 <- (rep(p, each=length(p)) + rep(p, times=length(p)))/2

h2 = 0.8
residualvar <- (var(parents) - h2*var(parents))/h2
residual <- rnorm(length(k0), 0, sqrt(residualvar))

k <- h2*k0 + residual 
## estimate R and S
R <- mean(k) - mean(parents)
S <- mean(p) - mean(parents)

R/S
plot(k, k0)

```

```{r, echo=FALSE}

hist(parents, breaks=100)
#plot(density(parents))
abline(v=qnorm(p=0.95), lty=2, lwd=3, col="red")
```

## Fig 11.1
```{r}
plot(k, k0)
```

## What is selection intensity

Selection intensity (symbolized by $i$) defined as the standardized selection differential $S/\sigma_P$.


```{r}
p2i <- function(p, n=1000, m=0, sd=1){
  parents <- rnorm(n, m, sd)
  cutoff <- quantile(parents, 1-p)
  S <- mean(parents[parents >= cutoff])
  return(S/sd)
}

myi <- data.frame()
for(p in seq(from=0.05, to=0.95, by=0.05)){
  tem <- data.frame(percent=p, i=p2i(p, n=10000))
  myi <- rbind(myi, tem)
}
```
