---
title: "Selection II"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Short-term Results

Variability of the responses:  
1. Random drift due to the restricted number of parents;   
2. Sampling error in estimating hte generation mean;  
3. Variation of selection differentials;  
4. Environmental factors.  

### Sampling variance
$$
\sigma_R^2 = \sigma_d^2 + \sigma_e^2  
= V_p(th^2/N_e + 1/M)
$$

In the equation, M denotes the of individuals measured.

> Selection experiments often yield no response over the first one or two generations, or even longer, but give a clear response later. The reason is usually that the numbers have been too small and random drift in the 'wrong' direction has nullified the response.

```{r}
c=5
i=1.271
h2=0.3
2*c^2/(i*h2)
```

### Reasons for Asymmetry of Response

1. Random Drift  
to do: simulate the response by considering drift.

3. Inbreeding Depression  
5. Genetic Asymmetry  
6. Genes with large effect  


> It is that if the character selected is a component of natural fitness, asymmetry should be expected, with selection towards increased fitness giving a slower response than selection towards decreased fitness.


## Long-term Results
